Lower Bounds on the Minimax Risk for the \\ Source Localization Problem

### 2017-02-05 paper.tex
WIP: Add appendix.

>>>>

In the integrator model of sensors, recall that the samples are given by
equation~\eqref{eq:samples-int-model}. We compute the SNR approximately at the
$k$-th sensor as follows. The power of the signal is given by
\begin{align}
	\abs{x_k(\theta)}^2 &= \abs*{\int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} x(s;\theta) ds.}^2 \\
	&\approx \abs*{\frac{S}{m} x\Big(\frac{kS}{m}; \theta\Big)}^2 \\
	&= \frac{S^2}{m^2} \abs*{x\Big(\frac{kS}{m}; \theta\Big)}^2
\end{align}
where in the approximation, we have assumed that the signal is roughly constant
in a small interval, taking the value of the signal at $s = kS/m$. The constant
itself is not relevant; it suffices to note at this point that the signal power
diminishes as $1/m^2$ since the sensor size \emph{must} diminish as $1/m$, if
the number of sensors has to increase to infinity.

The noise variance at the $k$-th sensor is computed similarly:
\begin{align}
	\mathbb E[\epsilon_k^2] &= \mathbb E \Bigg[ \bigg(\int_{(k-\frac{1}{2}S/m)}^{(k+\frac{1}{2}S/m)} \epsilon(s)\bigg)^2 \Bigg] \\
	&= \mathbb E \Bigg[ \int_{(k-\frac{1}{2}S/m)}^{(k+\frac{1}{2}S/m)} \epsilon(s) ds \int_{(k-\frac{1}{2}S/m)}^{(k+\frac{1}{2}S/m)} \epsilon(s') ds' \Bigg] \\
	&= \mathbb E \Bigg[ \int_{(k-\frac{1}{2}S/m)}^{(k+\frac{1}{2}S/m)} \int_{(k-\frac{1}{2}S/m)}^{(k+\frac{1}{2}S/m)} \epsilon(s) \epsilon(s') ds ds' \Bigg] \\
	&= \int_{(k-\frac{1}{2}S/m)}^{(k+\frac{1}{2}S/m)} \int_{(k-\frac{1}{2}S/m)}^{(k+\frac{1}{2}S/m)} \mathbb E[\epsilon(s) \epsilon(s')] ds ds' \\
	&= \int_{(k-\frac{1}{2}S/m)}^{(k+\frac{1}{2}S/m)} \int_{(k-\frac{1}{2}S/m)}^{(k+\frac{1}{2}S/m)} R_\epsilon(s, s') ds ds' \\
	&= \int_{(k-\frac{1}{2}S/m)}^{(k+\frac{1}{2}S/m)} \int_{(k-\frac{1}{2}S/m)}^{(k+\frac{1}{2}S/m)} \delta(s - s') ds ds' \\
	&= \int_{(k-\frac{1}{2}S/m)}^{(k+\frac{1}{2}S/m)} ds \\
	&= \frac{S}{m}
\end{align}
where $R_\epsilon(s, s') = \delta(s - s')$ is the autocorrelation function of
the white noise process.
